hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2025-03-10 inst/manuscript/paper.Rmd
add supplementary materials line
rerender with double spaces and move some figures for better spacing

---
title: ""
output: pdf_document
header-includes:
   - \usepackage{lineno}
   - \linenumbers
bibliography: ms_refs.bib
csl: apa.csl
---

@@

Following model selection, **hatchR** outputs results in two key locations: the `Phenology Summaries` tab, which provides a table with predictions for each spawn date, and the `Timeline Plot` tab, which shows the corresponding visualization of development timing. Both the prediction table and plot can be downloaded directly from their respective tabs. The full process is demonstrated through a detailed walkthrough on the **hatchR** Shiny website.

@@

We thank Laura Koller for her help designing the **hatchR** logo. Dan Isaak provided helpful discussion about model development and temperature data sets.

>>>>

---
title: ""
output: pdf_document
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
bibliography: ms_refs.bib
csl: apa.csl
---

@@

Following model selection, **hatchR** outputs results in two key locations: the `Phenology Summaries` tab, which provides a table with predictions for each spawn date, and the `Timeline Plot` tab, which shows the corresponding visualization of development timing. Both the prediction table and plot can be downloaded directly from their respective tabs. The full process is demonstrated through a detailed walkthrough in the supplementary video file (Supplementary Materials).

@@

We thank Laura Koller for her help designing the **hatchR** logo. Dan Isaak provided helpful discussion about model development and temperature data sets. Matt Kaylor provided useful comments on an earlier trial run of the package and shiny app.
